Respiratory-Related Mortality Rates Show A Positive Correlation With Increasing Air pollution

### 2024-04-02 paper/paper.qmd
testing graphs and models

```{r}
#| label: fig-all
#| fig-cap: Provincial Average PM2.5 Quantity Vs Total Deaths
#| echo: false
#| warning: false

breach_data %>%
  count(year) %>%
  ggplot(aes(x = year, y = n)) +
  geom_line() +
  labs(title = "Cyberattacks Over Time", x = "Year", y = "Number of Attacks")

@@

>>>>

```{r}
breach_data %>%
  count(year) %>%
  ggplot(aes(x = as.factor(year), y = n)) +  # Convert year to factor to treat it as discrete
  geom_line(group=1) +  # Ensure geom_line treats the data as connected points
  scale_x_discrete(breaks = levels(as.factor(breach_data$year))) +  # Specify breaks at every level of the factor
  labs(title = "Cyberattacks Over Time", x = "Year", y = "Number of Attacks") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))  # Rotate x labels to fit them all

@@

```
```{r}
ggplot(breach_data, aes(x = number_of_users_affected)) +
  stat_ecdf(geom = "step") +
  labs(title = "Cumulative Distribution of Number of Users Affected",
       x = "Number of Users Affected",
       y = "Cumulative Probability")
```
```{r}
breach_data %>%
  group_by(year) %>%
  summarize(total_users_affected = sum(number_of_users_affected, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = total_users_affected)) +
  geom_line() +
  labs(title = "Number of Users Affected Over Years",
       x = "Year",
       y = "Total Number of Users Affected") +
  theme_minimal()

```{r}
breach_data %>%
  ggplot(aes(x = sector, y = number_of_users_affected)) +
  geom_boxplot() +
  labs(title = "Spread of Number of Users Affected Across Sectors",
       x = "Sector",
       y = "Number of Users Affected") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
breach_data %>%
  ggplot(aes(x = number_of_users_affected)) +
  geom_histogram(bins = 30, fill = "blue", color = "black") +
  labs(title = "Distribution of Number of Users Affected by Cyberattacks",
       x = "Number of Users Affected",
       y = "Frequency") +
  theme_minimal()

```
```{r}
breach_data %>%
  filter(year == 2013) %>%
  summarise(
    median_users = median(number_of_users_affected, na.rm = TRUE),
    iqr_users = IQR(number_of_users_affected, na.rm = TRUE),
    upper_bound = median_users + 1.5 * iqr_users
  )

breach_data %>% filter(year == 2019)

breach_data %>%
  filter(year == 2019)%>%
  summarise(
    median_users = median(number_of_users_affected, na.rm = TRUE),
    iqr_users = IQR(number_of_users_affected, na.rm = TRUE),
    upper_bound = median_users + 1.5 * iqr_users
  )

```{r}
ggplot(breach_data, aes(x = log1p(number_of_users_affected))) +
  geom_density() +
  labs(x = "Log(Number of Users Affected + 1)", y = "Density") +
  theme_minimal()
```

```{r}
library(modelsummary)
lrmodel <- readRDS(file = here::here("models/lrmodel.rds"))

modelsummary(list("Linear Regression" = lrmodel))

ggplot(yearly_attacks, aes(x = year, y = number_of_attacks)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal() +
  labs(title = "Trend of Cyberattacks Over Years",
       x = "Year", y = "Number of Attacks")

library(broom)
# Augment the data with model diagnostics
augmented_data <- augment(lrmodel)

# Plot 1: Histogram of Residuals
ggplot(augmented_data, aes(x = .resid)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Histogram of Residuals", y = "Number of Occurrences", x = "Residuals")

# Plot 2: Residuals vs. Predictor Variable (year)
ggplot(augmented_data, aes(x = year, y = .resid)) +
  geom_point(color = "red") +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey") +
  theme_minimal() +
  labs(title = "Residuals vs. Year", y = "Residuals", x = "Year")

# Plot 3: Residuals vs. Fitted Values
ggplot(augmented_data, aes(x = .fitted, y = .resid)) +
  geom_point(color = "green") +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey") +
  theme_minimal() +
  labs(title = "Residuals vs. Fitted Values", y = "Residuals", x = "Fitted Values")

# Plot 4: Actual vs. Predicted Values
ggplot(augmented_data, aes(x = number_of_users_affected, y = .fitted)) +
  geom_point(color = "purple") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  theme_minimal() +
  labs(title = "Actual vs. Predicted Values", y = "Predicted", x = "Actual")

```{r}
liner_model <- readRDS(file = here::here("models/linear_model.rds"))

# Compare the actual outcomes with simulations from the posterior distribution
pp_check(liner_model) +
  theme_classic() +
  theme(legend.position = "bottom")
```

```{r}
augmented_data <- augment(sensitivity_model)

# Residuals vs. Fitted Values
ggplot(augmented_data, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal() +
  labs(title = "Residuals vs. Fitted Values", x = "Fitted Values", y = "Residuals")

# Actual vs. Predicted Values
ggplot(augmented_data, aes(x = number_of_users_affected, y = .fitted)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  theme_minimal() +
  labs(title = "Actual vs. Predicted Values", x = "Actual Values", y = "Predicted Values")
```

```{r}
cyberattack_neg_binomial <- readRDS(file = here::here("models/cyberattack_neg_binomial.rds"))
cyberattack_poisson <- readRDS(file = here::here("models/cyberattack_poisson.rds"))

#### Posterior Predictive Checks ####
# Poisson model
pp_poisson <- pp_check(cyberattack_poisson) + 
  theme(legend.position = "bottom") +
  labs(title = "Posterior Predictive Check for Poisson Model")

# Negative Binomial model
pp_neg_binomial <- pp_check(cyberattack_neg_binomial) + 
  theme(legend.position = "bottom") +
  labs(title = "Posterior Predictive Check for Negative Binomial Model")

# Display the plots
print(pp_poisson)
print(pp_neg_binomial)

```{r}
library(ggplot2)
library(dplyr)
library(forcats) # For fct_collapse

# Assuming breach_data is already loaded and has columns named 'year', 'country', and 'frequency'
# and frequency is already calculated

# Prepare the dataset
breach_data_summary <- breach_data %>%
  mutate(country = fct_collapse(country,
                                "Other countries" = setdiff(unique(country), 
                                                              c("USA", "Australia", "Canada", "Global", "Japan", "UK")))) %>%
  group_by(year, country) %>%
  summarize(frequency = n(), .groups = 'drop')

# Separating the data by country for ease of plotting
country_data <- breach_data_summary %>%
  filter(country %in% c("Australia", "Canada", "Global", "Japan", "UK", "Other countries"))

usa_data <- breach_data_summary %>%
  filter(country == "USA")

# Find the max frequency for USA to scale the secondary axis accordingly
max_usa_frequency <- max(usa_data$frequency)

# Define a color palette
color_palette <- c("Australia" = "#1b9e77", "Canada" = "#d95f02", "Global" = "#7570b3", "Japan" = "#e7298a", "UK" = "#66a61e", "Other countries" = "#e6ab02", "USA" = "#666666")

# Plot
gg <- ggplot() +
  # Add bar plots for all countries except USA
  geom_bar(data = country_data, aes(x = as.factor(year), y = frequency, fill = country), stat = "identity", position = "dodge") +
  # Add line for USA with points
  geom_line(data = usa_data, aes(x = as.factor(year), y = frequency), color = color_palette["USA"]) +
  geom_point(data = usa_data, aes(x = as.factor(year), y = frequency), color = color_palette["USA"]) +
  # Add primary y-axis for "Other countries"
  scale_y_continuous(name = "Frequency of Cyber Attacks (Other Countries)", labels = scales::comma) +
  # Add secondary y-axis for USA
  scale_y_continuous(name = "Frequency of Cyber Attacks (USA)",
                     sec.axis = sec_axis(~ . * max_usa_frequency / max(breach_data_summary$frequency), name = "USA", labels = scales::comma)) +
  # Set the breaks for x-axis to every year level
  scale_x_discrete(breaks = levels(as.factor(breach_data$year))) +
  scale_fill_manual(values = color_palette) +
  labs(title = "Overview of Cyber Attacks by Year and Country",
       subtitle = "Bar plots for countries; line plot for USA scaled on secondary axis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), # Rotate x-axis labels
        legend.position = "bottom") # Adjust the position of the legend

# Print the plot
print(gg)

# Save the plot
ggsave("cyber_attacks_overview.png", plot = gg, width = 12, height = 8, dpi = 300)

library(ggplot2)
library(dplyr)
library(forcats) # For fct_collapse to group levels into "Other countries"

# Assuming breach_data is already loaded and has columns named 'year', 'country', and 'frequency'
# and frequency is already calculated (e.g., it is not just a raw count of rows)

# Prepare the dataset
breach_data_summary <- breach_data %>%
  mutate(country = fct_collapse(country,
                                "Other countries" = setdiff(unique(country), 
                                                              c("USA", "Australia", "Canada", "Global", "Japan", "UK")))) %>%
  group_by(year, country) %>%
  summarize(frequency = n(), .groups = 'drop')

# Separating the data by country for ease of plotting
country_data <- breach_data_summary %>%
  filter(country %in% c("Australia", "Canada", "Global", "Japan", "UK", "Other countries"))

usa_data <- breach_data_summary %>%
  filter(country == "USA")

# Find the max frequency for USA to scale the secondary axis accordingly
max_usa_frequency <- max(usa_data$frequency)

# Plot
gg <- ggplot() +
  # Add bar plots for all countries except USA
  geom_bar(data = country_data, aes(x = as.factor(year), y = frequency, fill = country), stat = "identity", position = "dodge") +
  # Add line for USA with points
  geom_line(data = usa_data, aes(x = as.factor(year), y = frequency), color = "blue") +
  geom_point(data = usa_data, aes(x = as.factor(year), y = frequency), color = "blue") +
  # Add primary y-axis for "Other countries"
  scale_y_continuous(name = "Frequency of Cyber Attacks (Other Countries)") +
  # Add secondary y-axis for USA
  scale_y_continuous(name = "Frequency of Cyber Attacks (USA)",
                     sec.axis = sec_axis(~ . * max_usa_frequency / max(breach_data_summary$frequency), name = "USA")) +
  # Set the breaks for x-axis to every year level
  scale_x_discrete(breaks = levels(as.factor(breach_data$year))) +
  scale_fill_manual(values = c("Australia" = "color1", "Canada" = "color2", "Global" = "color3", "Japan" = "color4", "UK" = "color5", "Other countries" = "color6")) +
  labs(title = "Overview of Cyber Attacks by Year and Country",
       subtitle = "Bar plots for countries; line plot for USA scaled on secondary axis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), # Rotate x-axis labels
        legend.position = "bottom") # Adjust the position of the legend

# Print the plot
print(gg)

Make sure to replace "color1", "color2", etc., with the actual colors you want for the bars. Adjust the names of the columns if needed, based on your dataset. The `scale_y_continuous` for the USA might need to be adjusted based on the actual frequencies in your dataset. The `sec.axis` function is used to create the secondary
